---
title: "Helpfulness Clothing, Shoes and Jewelry"
author: "zdenek.vesely@gmail.com"
date: "1/20/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r data, include=FALSE}
library(tidyverse)
library(readr)
library(lubridate)
library(kableExtra)

review_data <- read_rds("prepared_data/reviews_enriched_clothing_all.Rds")
N_OBS_WORD = 2000


MAIN_LABEL <- " Clothing, Shoes and Jewelry"

review_data <-
  review_data %>% 
  mutate(helpful_positive_1 = 1 * (helpful_positive >= 3 & helpful_perc >= 0.8),
         helpful_negative_1 = 1 * (helpful_negative >= 3 & helpful_perc <= 0.2))
```

Each review can have up-votes (= positive votes) or down-votes (= negative votes).

My personal definition:

 *  the review is helpful positive if it has at least 3 up-votes and there is at least 80% positive votes
 *  the review is helpful negative (spam) if it has at least 3 down-votes and there is at least 80% negative votes

## Helpfulness by stars

Large percentage of the reviews has no helpful score:

```{r zero_help}
hepful_by_stars <-
  review_data %>% 
  group_by(stars = overall) %>% 
  summarise(helpful_positive_n = sum(helpful_positive_1),
            helpful_positive_perc = mean(helpful_positive_1),
            helpful_negative_n = sum(helpful_negative_1),
            helpful_negative_perc = mean(helpful_negative_1),
            n_reviews = length(overall)) 

hepful_by_stars %>% 
  kable(digits = 2) %>% 
  kable_styling(c("striped", "bordered"))

hepful_by_stars %>% 
  gather(-1, key = "helpful", value = "perc") %>% 
  filter(helpful %in% c("helpful_positive_perc", "helpful_negative_perc")) %>% 
  ggplot() + 
  geom_col(aes(y = perc, x = stars, group = helpful, fill = helpful),
           position = "dodge") +
  scale_y_continuous(labels = scales::percent) +
  ylab("share of helpful reviews") +
  ggtitle(MAIN_LABEL)
#todo: by category
```


## Words (tokens)  {.tabset .tabset-fade .tabset-pills}

We can tokenize the review texts and look into what kind of words are associated with positive/negative reviews or with helpful/spam reviews.

```{r words}
tokens_data <-
  review_data %>% 
  select(review_tokens, overall, helpful_positive_1, helpful_negative_1) %>% 
  unnest(review_tokens) %>% 
  group_by(review_tokens) %>% 
  summarise(stars = mean(overall),
            helpful_positive_1 = mean(helpful_positive_1),
            helpful_negative_1= mean(helpful_negative_1),
            n_obs = length(review_tokens)) %>% 
  filter(n_obs >= N_OBS_WORD) 

tokens_data_rows <- nrow(tokens_data)
```

### Stars
The most positive and most negative frequent words:
```{r tokens_stars}
N_ROWS = 15
tokens_data %>% 
  arrange(-stars) %>% 
  slice(c(1:N_ROWS, (tokens_data_rows - N_ROWS + 1):tokens_data_rows)) %>% 
  kable(digits = 4) %>% 
  kable_styling("striped", full_width = F) %>%
  row_spec((N_ROWS + 1):(2*N_ROWS), color = "white", background = "#D7261E")
```

### Helpful positive
The most and least helpful frequent words:
```{r tokens_help_pos}
N_ROWS = 15
tokens_data %>% 
  arrange(-helpful_positive_1)  %>% 
  slice(c(1:N_ROWS, (tokens_data_rows - N_ROWS + 1):tokens_data_rows)) %>% 
  kable(digits = 4) %>% 
  kable_styling("striped", full_width = F) %>%
  row_spec((N_ROWS + 1):(2*N_ROWS), color = "white", background = "#D7261E")
```

### Helpful negative
The most and least spam related frequent words:
```{r tokens_help_neg, warning=FALSE, message=FALSE}
N_ROWS = 15
tokens_data %>% 
  arrange(-helpful_negative_1)  %>% 
  slice(c(1:N_ROWS, (tokens_data_rows - N_ROWS + 1):tokens_data_rows)) %>% 
  kable(digits = 4) %>% 
  kable_styling("striped", full_width = F) %>%
  row_spec((N_ROWS + 1):(2*N_ROWS), color = "white", background = "#D7261E")
```

```{r free_memory}
rm("tokens_data")
```


## Review length {.tabset .tabset-fade .tabset-pills}

Distribution of the review length.

### Stars

```{r length_stars, warning=FALSE, message=FALSE}
review_data %>% 
  mutate(stars = factor(overall)) %>% 
  ggplot(aes(x = review_words, fill = stars, group = stars)) +
  geom_density(aes(y = ..density..), alpha = 0.4) +
  scale_x_log10(limits = c(1, 10000)) +
  ylab("density") +
  xlab("# words per review") +
  ggtitle(MAIN_LABEL)

```

### Helpfulness positive

```{r length_help_pos}
review_data %>% 
  mutate(helpful_positive_1 = factor(helpful_positive_1)) %>% 
  ggplot(aes(x = review_words, fill = helpful_positive_1, group = helpful_positive_1)) +
  geom_density(aes(y = ..density..), alpha = 0.4) +
  scale_x_log10(limits = c(1, 10000)) +
  ylab("density") +
  xlab("# words per review") +
  ggtitle(MAIN_LABEL)
```

### Helpfulness negative

```{r length_help_neg, warning=FALSE, message=FALSE}
review_data %>% 
  mutate(helpful_negative_1 = factor(helpful_negative_1)) %>% 
  ggplot(aes(x = review_words, fill = helpful_negative_1, group = helpful_negative_1)) +
  geom_density(aes(y = ..density..), alpha = 0.4) +
  scale_x_log10(limits = c(1, 10000)) +
  ylab("density") +
  xlab("# words per review") +
  ggtitle(MAIN_LABEL)
```

## Review time order {.tabset .tabset-fade .tabset-pills}

We can order reviews for one products in time.

Review order: order of the review of the given product (number from 1, ...)

Relative review time: $\frac{\text{Review order} - 1/2}{\# \text{reviews of given products}}$


### Stars

```{r time_stars}
review_data %>% 
   mutate(stars = factor(overall),
         relative_review_time = (time_order_per_asin-1/2)/n_rev_per_asin) %>% 
  ggplot(aes(x = relative_review_time, fill = stars)) +
  geom_bar(position="fill", stat="bin", bins = 50) +
  scale_y_continuous(labels = scales::percent) +
  ylab("share") +
  xlab("relative review time") +
  ggtitle(MAIN_LABEL)
```


### Positive helpful

```{r time_pos}
review_data %>% 
   mutate(helpful_positive_1 = factor(helpful_positive_1),
         relative_review_time = (time_order_per_asin-1/2)/n_rev_per_asin) %>% 
  ggplot(aes(x = relative_review_time, fill = helpful_positive_1)) +
  geom_bar(position="fill",  stat="bin", bins = 50) +
  scale_y_continuous(labels = scales::percent) +
  coord_cartesian(ylim = c(0, 0.5)) +
  ylab("share") +
  xlab("relative review time") +
  ggtitle(MAIN_LABEL)
```

### Negative helpful

```{r time_negative}
review_data %>% 
   mutate(helpful_negative_1 = factor(helpful_negative_1),
         relative_review_time = (time_order_per_asin-1/2)/n_rev_per_asin) %>% 
  ggplot(aes(x = relative_review_time, fill = helpful_negative_1)) +
  geom_bar(position="fill",  stat="bin", bins = 50) +
  scale_y_continuous(labels = scales::percent) +
  coord_cartesian(ylim = c(0, 0.08)) +
  ylab("share") +
  xlab("relative review time") +
  ggtitle(MAIN_LABEL)
```



## Price {.tabset .tabset-fade .tabset-pills}

The product prices distribution:

```{r hist_price}
product_data <-
  review_data %>% 
  group_by(asin) %>% 
  summarise(price = first(price),
            n_rev_per_asin = first(n_rev_per_asin),
            stars = first(avg_overall_per_asin),
            avg_helpful_positive_1 = mean(helpful_positive_1),
            n_helpful_positive_1 = sum(helpful_positive_1),
            bought_together = first(bought_together))

price_limits <- 
  product_data %>% 
  pull(price) %>% 
  quantile(c(0.005, 0.995), na.rm = TRUE)

product_data %>% 
  filter(price >= price_limits[1],
         price <= price_limits[2]) %>% 
  ggplot() +
  geom_histogram(aes(x = price), bins = 100, fill = "#2ab7ca") +
  coord_cartesian(xlim = price_limits) +
  ylab("# products") + 
  xlab("product price") +
  ggtitle(MAIN_LABEL)
```


### Stars

```{r price_stars}
review_data %>% 
  mutate(stars = factor(overall)) %>% 
  ggplot(aes(x = price, fill = stars)) +
  geom_bar(position="fill",  stat="bin", bins = 50) +
  scale_x_log10(limits = price_limits) +
  ylab("share") +
  xlab("product price") +
  ggtitle(MAIN_LABEL)
  
```


### Positive helpful

```{r price_pos}
review_data %>% 
  mutate(helpful_positive_1 = factor(helpful_positive_1)) %>% 
  ggplot(aes(x = price, fill = helpful_positive_1)) +
  geom_bar(position="fill", stat="bin", bins = 50) +
  scale_x_log10(limits = price_limits) +
  scale_y_continuous(labels = scales::percent) +
  coord_cartesian(ylim = c(0, 0.5)) +
  ggtitle(MAIN_LABEL)
```

### Negative helpful

```{r price_negative}
review_data %>% 
  mutate(helpful_negative_1 = factor(helpful_negative_1)) %>% 
  ggplot(aes(x = price, fill = helpful_negative_1)) +
  geom_bar(position="fill",  stat="bin", bins = 50) +
  scale_x_log10(limits = price_limits) +
  scale_y_continuous(labels = scales::percent) +
  coord_cartesian(ylim = c(0, 0.10)) +
  ylab("share") +
  xlab("product price") +
  ggtitle(MAIN_LABEL)
```


## Per products view {.tabset .tabset-fade .tabset-pills}

###  Number of positive reviews vs total number of reviews 

As expected - the more reviews, the more positive reviews. But there are saturation limits as only limited top reviews are shown on each product page.

```{r helpful_n_share}
limits_n_rev <- product_data %>% 
  pull(n_rev_per_asin) %>% 
  quantile(c(0.0075, 0.9925))

product_data %>% 
  mutate(avg_stars = factor(round(stars, 0))) %>% 
  ggplot(aes(x = n_rev_per_asin, y = n_helpful_positive_1,
             group = avg_stars, color = avg_stars, fill = avg_stars)) +
  geom_smooth(method = "loess", se = TRUE) +
  scale_x_continuous(limits = limits_n_rev) +
  #scale_x_log10(limits = limits_n_rev) +
  xlab("# reviews per product") + 
  ylab("# helpful reviews per product") + 
  labs(fill = "Average stars") +
  guides(colour = FALSE) +
  ggtitle(MAIN_LABEL)
```


###  Reviews per product on price

The higher price, the lower sales are expected. Therefore the lower number of reviews.

```{r n_rev_price}
product_data %>% 
  ggplot(aes(x = price, y = n_rev_per_asin)) +
  geom_smooth(method = "loess", se = TRUE) +
  scale_x_log10(limits = price_limits) +
  expand_limits(y = 1) +
  ylab("# reviews per product") +
  xlab("product price") +
  ggtitle(MAIN_LABEL)
```


## Product pairs

Attribute "bought_together" in the products metadata shows which products are often bought together (in one basket) with the given product.
For each product having this attribute we can calculate average price, review score (stars) and review helpfulness of the related products.

```{r product_pairs}
product_pairs <-
  product_data %>% 
  select(asin1 = asin, 
         asin2 = bought_together) %>% 
  filter(map(asin2, ~!is.null(.[[1]])) %>% as.logical()) %>% 
  unnest(asin2)

products_pairs_data <-
  product_data %>% 
  inner_join(product_pairs, 
            by = c("asin" = "asin1")) %>% 
  left_join(product_data,
            by = c("asin2" = "asin"), 
            suffix = c("", "_rel")
            ) %>% 
  group_by(asin) %>% 
  summarise(price = first(price),
            n_rev_per_asin = first(n_rev_per_asin),
            stars  = first(stars),
            avg_helpful_positive_1 = first(avg_helpful_positive_1),
            n_helpful_positive_1 = first(n_helpful_positive_1),
            price_rel = mean(price_rel, na.rm = TRUE),
            n_rev_per_asin_rel = mean(n_rev_per_asin_rel, na.rm = TRUE),
            stars_rel = mean(stars_rel, na.rm = TRUE),
            avg_helpful_positive_1_rel = mean(avg_helpful_positive_1_rel, na.rm = TRUE),
            n_helpful_positive_1_rel = mean(n_helpful_positive_1_rel, na.rm = TRUE))

# 
# products_pairs_data %>% 
#   summarise(mean(is.na(price_rel)))
# 
# products_pairs_data %>% 
#   summarise(mean(is.na(n_rev_per_asin)))


products_pairs_data %>% 
  ggplot(aes(x = stars , y = stars_rel)) +
  geom_smooth(method = "loess", se = TRUE) +
  expand_limits(y = 0) + 
  xlab("average product score (stars)") +
  ylab("related (bought together) product average score (stars)") +
  geom_abline(slope = 1, col = "gray") +
  ggtitle(MAIN_LABEL)

products_pairs_data %>% 
  ggplot(aes(x =  avg_helpful_positive_1, y = avg_helpful_positive_1_rel)) +
  geom_smooth(method = "loess", se = TRUE) +
  expand_limits(y = 0) + 
  xlab("average reviews helpfulness") +
  ylab("related (bought together) product average reviews helpfulness") +
  scale_x_continuous(labels = scales::percent) + 
  scale_y_continuous(labels = scales::percent) +
  geom_abline(slope = 1, col = "gray") +
  ggtitle(MAIN_LABEL)

```
