---
title: "Helpfulness Electronics"
author: "zdenek.vesely@gmail.com"
date: "1/20/2020"
output: html_document
editor_options: 
  chunk_output_type: console
params:
  data_size: "small"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```


```{r data, include=FALSE}
library(tidyverse)
library(readr)
library(lubridate)
library(kableExtra)

if (params$data_size == "small") {
  review_data <- read_rds("prepared_data/reviews_enriched_electronics_10000.Rds")
  N_OBS_WORLD = 1000
} else {
  review_data <- read_rds("prepared_data/reviews_enriched_electronics_all.Rds")
  N_OBS_WORLD = 4000
}


review_data <-
  review_data %>% 
  mutate(helpful_positive_1 = 1 * (helpful_positive >= 3 & helpful_perc >= 0.8),
         helpful_negative_1 = 1 * (helpful_negative >= 3 & helpful_perc <= 0.2))
```

Each review can have up-votes (= positive votes) or down-votes (= negative votes).

My personal definition:

 *  the review is helpful positive if it has at least 3 up-votes and there is at least 80% positive votes
 *  the review is helpful negative (spam) if it has at least 3 down-votes and there is at least 80% negative votes

## Helpfulness by stars

Large percentage of the reviews has no helpful score:

```{r zero_help}
hepful_by_stars <-
  review_data %>% 
  group_by(stars = overall) %>% 
  summarise(helpful_positive_n = sum(helpful_positive_1),
            helpful_positive_perc = mean(helpful_positive_1),
            helpful_negative_n = sum(helpful_negative_1),
            helpful_negative_perc = mean(helpful_negative_1),
            n_reviews = length(overall)) 

hepful_by_stars %>% 
  knitr::kable(digits = 2)

hepful_by_stars %>% 
  gather(-1, key = "helpful", value = "perc") %>% 
  filter(helpful %in% c("helpful_positive_perc", "helpful_negative_perc")) %>% 
  ggplot() + 
  geom_col(aes(y = perc, x = stars, group = helpful, fill = helpful),
           position = "dodge") +
  scale_y_continuous(labels = scales::percent)
#todo: by category
```

The more positive reviews tend to be more helpful.

The negative reviews tent to be down-voted.

## Words (tokens)  {.tabset .tabset-fade .tabset-pills}

We can tokenize the review texts and look into what kind of words are associated with positive/negative reviews or with helpful/spam reviews.

```{r words}
tokens_data <-
  review_data %>% 
  select(review_tokens, overall, helpful_positive_1, helpful_negative_1) %>% 
  unnest(review_tokens) %>% 
  group_by(review_tokens) %>% 
  summarise(stars = mean(overall),
            helpful_positive_1 = mean(helpful_positive_1),
            helpful_negative_1= mean(helpful_negative_1),
            n_obs = length(review_tokens)) %>% 
  filter(n_obs >= N_OBS_WORLD) 

tokens_data_rows <- nrow(tokens_data)
```

### Stars
The most positive and most negative frequent words:
```{r tokens_stars}
N_ROWS = 15
tokens_data %>% 
  arrange(-stars) %>% 
  slice(c(1:N_ROWS, (tokens_data_rows - N_ROWS + 1):tokens_data_rows)) %>% 
  kable(digits = 4) %>% 
  kable_styling("striped", full_width = F) %>%
  row_spec((N_ROWS + 1):(2*N_ROWS), color = "white", background = "#D7261E")
```

### Helpful positive
The most and least helpful frequent words:
```{r tokens_help_pos}
N_ROWS = 15
tokens_data %>% 
  arrange(-helpful_positive_1)  %>% 
  slice(c(1:N_ROWS, (tokens_data_rows - N_ROWS + 1):tokens_data_rows)) %>% 
  kable(digits = 4) %>% 
  kable_styling("striped", full_width = F) %>%
  row_spec((N_ROWS + 1):(2*N_ROWS), color = "white", background = "#D7261E")
```

### Helpful negative
The most and least spam related frequent words:
```{r tokens_help_neg, warning=FALSE, message=FALSE}
N_ROWS = 15
tokens_data %>% 
  arrange(-helpful_negative_1)  %>% 
  slice(c(1:N_ROWS, (tokens_data_rows - N_ROWS + 1):tokens_data_rows)) %>% 
  kable(digits = 4) %>% 
  kable_styling("striped", full_width = F) %>%
  row_spec((N_ROWS + 1):(2*N_ROWS), color = "white", background = "#D7261E")
```

## Review length {.tabset .tabset-fade .tabset-pills}

### Stars

```{r length_stars, warning=FALSE, message=FALSE}
review_data %>% 
  mutate(stars = factor(overall)) %>% 
  ggplot(aes(x = review_words, fill = stars, group = stars)) +
  geom_density(aes(y = ..density..), alpha = 0.4) +
  scale_x_log10(limits = c(1, 10000)) 

```

### Helpfulness positive

```{r length_help_pos}
review_data %>% 
  mutate(helpful_positive_1 = factor(helpful_positive_1)) %>% 
  ggplot(aes(x = review_words, fill = helpful_positive_1, group = helpful_positive_1)) +
  geom_density(aes(y = ..density..), alpha = 0.4) +
  scale_x_log10(limits = c(1, 10000))
```

### Helpfulness negative

```{r length_help_neg, warning=FALSE, message=FALSE}
review_data %>% 
  mutate(helpful_negative_1 = factor(helpful_negative_1)) %>% 
  ggplot(aes(x = review_words, fill = helpful_negative_1, group = helpful_negative_1)) +
  geom_density(aes(y = ..density..), alpha = 0.4) +
  scale_x_log10(limits = c(1, 10000))
```

## Review time order {.tabset .tabset-fade .tabset-pills}

We can order reviews for one products in time.

Review order: order of the review of the given product (number from 1, ...)

Relative review time: (Review order - 1/2) / # reviews of given products

### Stars

```{r time_stars}
review_data %>% 
   mutate(stars = factor(overall),
         relative_review_time = (time_order_per_asin-1/2)/n_rev_per_asin) %>% 
  ggplot(aes(x = relative_review_time, fill = stars)) +
  geom_bar(position="fill", stat="bin", bins = 50) +
  scale_y_continuous(labels = scales::percent)
```


### Positive helpful

```{r time_pos}
review_data %>% 
   mutate(helpful_positive_1 = factor(helpful_positive_1),
         relative_review_time = (time_order_per_asin-1/2)/n_rev_per_asin) %>% 
  ggplot(aes(x = relative_review_time, fill = helpful_positive_1)) +
  geom_bar(position="fill",  stat="bin", bins = 50) +
  scale_y_continuous(labels = scales::percent) +
  coord_cartesian(ylim = c(0, 0.5))
```

### Negative helpful

```{r time_negative}
review_data %>% 
   mutate(helpful_negative_1 = factor(helpful_negative_1),
         relative_review_time = (time_order_per_asin-1/2)/n_rev_per_asin) %>% 
  ggplot(aes(x = relative_review_time, fill = helpful_negative_1)) +
  geom_bar(position="fill",  stat="bin", bins = 50) +
  scale_y_continuous(labels = scales::percent) +
  coord_cartesian(ylim = c(0, 0.03))

```



## Price {.tabset .tabset-fade .tabset-pills}

### Stars

```{r price_stars}
limits_x <- c(1, 500)

review_data %>% 
  mutate(stars = factor(overall)) %>% 
  ggplot(aes(x = price, fill = stars)) +
  geom_bar(position="fill",  stat="bin", bins = 50) +
  scale_x_log10(limits = limits_x)
```


### Positive helpful

```{r price_pos}
review_data %>% 
  mutate(helpful_positive_1 = factor(helpful_positive_1)) %>% 
  ggplot(aes(x = price, fill = helpful_positive_1)) +
  geom_bar(position="fill", stat="bin", bins = 50) +
  scale_x_log10(limits = limits_x) +
  coord_cartesian(ylim = c(0, 0.5))
```

### Negative helpful

```{r price_negative}
review_data %>% 
  mutate(helpful_negative_1 = factor(helpful_negative_1)) %>% 
  ggplot(aes(x = price, fill = helpful_negative_1)) +
  geom_bar(position="fill",  stat="bin", bins = 50) +
  scale_x_log10(limits = limits_x) +
  coord_cartesian(ylim = c(0, 0.03))
```